---
title: "Graph Configuration Model based Evaluation of the Education-Occupation Match"
subtitle: "related R codes"
author: Laszlo Gadar, Janos Abonyi
date: 01/02/2017
output: pdf_document
always_allow_html: yes
---

#Packages

```{r setup, echo=F, warning=F, message=F}
library(dplyr)
library(plyr)
library(reshape2)
library(ggplot2)
library(ggdendro)
library(ggalt) #for dumbbell figure
library(ggrepel)
library(scales)
library(igraph)
library(poweRlaw)
library(knitr)
library(cluster)
library(lpbrim)
library(seriation)
library(readxl)
```



#1. Load data

```{r create_dataframe_and_graph, echo=F, warning=F, message=F}
db<-read.csv("E:/Dropbox/GL_AJ_Edumining/Cikk_0_PLOS_ONE/file/graph_of_hungarian_HE.csv", sep=";", header=T, encoding = "ISO-8859-3", na.strings="NA", stringsAsFactors = F)

edges<-db %>% filter(Grad_level=="B") %>% select(Pr_ENG_bachelor,ISCO3)

g<-graph.data.frame(edges, directed = F)
V(g)$type<-V(g)$name %in% edges[,2]

A<-get.incidence(g)

g.sim <- simplify(g) #unweighted graph
A.sim <- get.incidence(g.sim)
```

#2. Descriptive statistics

##2.1. Number of factor levels of variables
```{r}
length(unique(db$ID))
length(unique(db$Gender))
length(unique(db$Inst_HUN))
length(unique(db$Pr_area_ENG))
length(unique(db$Pr_HUN))
length(unique(db$Pr_ENG_bachelor))
length(unique(db$Grad_level))
length(unique(db$FEOR4))
length(unique(db$FEOR3))
length(unique(db$ISCO1))
length(unique(db$ISCO3))
length(unique(db$Req_HEd))
length(unique(db$Head_couty_HUN))
length(unique(db$Weekly_hrs))
length(unique(db$Mountly_wage_HUF))
```

##2.2. Number of graduates in different groups
```{r, echo=F}
nrow(db) #number of gradautes who has occupational data

table(db$Grad_level) #number of graduates on different educational level

length(unique(db[db$Grad_level=="B", "Inst_HUN"])) #number of institutions of bachelor graduates
length(unique(db[db$Grad_level=="B", "Pr_area_ENG"])) #number of training program areas of bachelor graduates
length(unique(db[db$Grad_level=="B", "Pr_ENG_bachelor"])) #number of programs of bachelor graduates
length(unique(db[db$Grad_level=="B", "FEOR4"])) #number of 4th level occupations (ISCO) of bachelor graduates
length(unique(db[db$Grad_level=="B", "FEOR3"])) #number of 3th level occupations (ISCO) of bachelor graduates
```

##2.3 Distribution of graduates working in occupation category that requires higher education degree
```{r, echo=F}
prop.table(table(db$Grad_level, db$Req_HEd),1)
```

0: occupations that does NOT require higher education
1: occupations that does require higher education

A: higher vocational trainings
B: bachelor
E: univerity (before Bologna)
F: collage (before Bologna)
M: master
O: undivided training (e.g loyar, doctor)
P: special teacher training

##2.4. Distribution of bachelor graduates working in an occupation that requires higher education degree (Fig1)

```{r shankey_data, echo=F}
db_bachelor <- db %>% filter(Grad_level=="B")

link1 <- as.data.frame(table(db_bachelor$Pr_area_ENG, db_bachelor$Req_HEd))
link1$Var1 <- as.character(link1$Var1)
link1$Var2 <- as.character(link1$Var2)
link1[link1$Var2==0,2] <- c("not require")
link1[link1$Var2==1,2] <- c("require")

link2 <- as.data.frame(table(db_bachelor$Req_HEd, db_bachelor$ISCO1_ENG))
link2$Var1 <- as.character(link2$Var1)
link2$Var2 <- as.character(link2$Var2)
link2[link2$Var1==0,1] <- c("not require")
link2[link2$Var1==1,1] <- c("require")

link <- rbind(link1, link2)
link$Var1 <- as.character(link$Var1)
link$Var2 <- as.character(link$Var2)
link <- link[link$Freq>0,]

#write.csv2(link, "link.csv") #shankey figure made with http://sankeymatic.com/build/

prop.table(table(db_bachelor$Pr_area_ENG, db_bachelor$Req_HEd),1)
```

##2.5. Distribution of graduates that work on occupation which requiring higher education degree by counties in Hungary (Fig2)

```{r, echo=F}
table(db_bachelor$NUTS_region, db_bachelor$Req_HEd)
#write.csv2(prop.table(table(db_bachelor$Head_couty_HUN, db_bachelor$Req_HEd),1), file="prop.county.csv", sep=";")
```

##2.6. Gender pay gap (Fig.3, Fig.4)

Lollipop chart on wage differences by gender

```{r, echo=F}
#https://www.r-bloggers.com/beating-lollipops-into-dumbbells/

db.l <- db[db$Grad_level=="B" & db$Weekly_hrs>36 & db$Mountly_wage_HUF>93000, c("Gender", "Mountly_wage_HUF", "Pr_area_ENG")]

db.l <- aggregate(Mountly_wage_HUF ~ Gender + Pr_area_ENG, db.l, median)
db.l <- dcast(db.l, Pr_area_ENG ~ Gender)
colnames(db.l)[c(3,2)] <- c("Male", "Female")
#db.l <- db.l[,c(1,3,2)]
db.l$diff <- db.l$Male-db.l$Female
db.l <- arrange(db.l, desc(Male))
db.l[1,1] <- "Computer Science and IT"
db.l <- mutate(db.l, Pr_area_ENG=factor(Pr_area_ENG,
                                           levels=rev(Pr_area_ENG)))
```

```{r income_gap_by_pr, echo=F, dpi=300, warning=F}
ggplot(db.l, aes(x=Female, xend=Male, y=Pr_area_ENG)) + 
  geom_dumbbell(colour="#686868",
                colour_x="red", 
                colour_xend="blue", 
                size_x=4, 
                size_xend=4) + 
  scale_x_continuous(breaks=seq(100000, 300000, by=50000), 
                     labels=sprintf("%s HUF", comma(seq(100000, 300000, by=50000)))) + 
  geom_text(data=filter(db.l, Pr_area_ENG=="Computer Science and IT"),
                     aes(x=Female, y=Pr_area_ENG, label="Female"),
                     color="red", size=3, vjust=-2, fontface="bold") +
  geom_text(data=filter(db.l, Pr_area_ENG=="Computer Science and IT"),
                     aes(x=Male, y=Pr_area_ENG, label="Male"),
                     color="blue", size=3, vjust=-2, fontface="bold") +
  theme_bw() + 
  theme(axis.ticks=element_blank()) +
  theme(panel.grid.minor=element_blank()) + 
  theme(panel.border=element_blank()) + 
  labs(y=NULL, x=NULL)

#ggsave("Fig4.eps", width = 13.2, units="cm")
```


```{r, echo=F}
db.l <- db[db$Grad_level=="B" & db$Weekly_hrs>36 & db$Mountly_wage_HUF>93000, c("Gender", "Mountly_wage_HUF", "ISCO1")]
db.l$ISCO1 <- as.character(db.l$ISCO1)

db.l <- aggregate(Mountly_wage_HUF ~ Gender + ISCO1, db.l, median)
db.l <- dcast(db.l, ISCO1 ~ Gender)
colnames(db.l)[c(3,2)] <- c("Male", "Female")

db.l$diff <- db.l$Male-db.l$Female
db.l <- arrange(db.l, desc(Male))

db.l <- mutate(db.l, ISCO1=factor(ISCO1,levels=rev(ISCO1)))
```

```{r income_gap_by_oc, echo=F, dpi=300}
ggplot(db.l, aes(x=Female, xend=Male, y=ISCO1)) + 
  geom_dumbbell(color="#686868", 
                colour_x="red", 
                colour_xend="blue", 
                size_x=4, 
                size_xend=4) + 
  scale_x_continuous(breaks=seq(100000, 300000, by=50000), 
                     labels=sprintf("%s HUF", comma(seq(100000, 300000, by=50000)))) + 
  geom_text(data=filter(db.l, ISCO1=="1"),
                     aes(x=Female, y=ISCO1, label="Female"),
                     color="red", size=3, vjust=-2, fontface="bold") +
  geom_text(data=filter(db.l, ISCO1=="1"),
                     aes(x=Male, y=ISCO1, label="Male"),
                     color="blue", size=3, vjust=-2, fontface="bold") +
  theme_bw() + 
  theme(axis.ticks=element_blank()) +
  theme(panel.grid.minor=element_blank()) + 
  theme(panel.border=element_blank()) + 
  labs(y=NULL, x=NULL)

#ggsave("Fig5.eps", width = 13.2, units="cm")
```

##2.7. Strongest connections (Table4)

```{r, echo=F, warning=F}
DF.pur <- melt(A)
DF.pur <- DF.pur[DF.pur$value!=0,]
DF.pur$Var2 <- as.factor(DF.pur$Var2)

degree.tr <- data.frame(rownames(A),rowSums(A))
names(degree.tr) <- c("names", "degree.tr")
degree.oc <- data.frame(colnames(A),colSums(A))
names(degree.oc) <- c("names", "degree.oc")

DF.pur <- left_join(DF.pur, degree.tr, by=c("Var1"="names"))
DF.pur <- left_join(DF.pur, degree.oc, by=c("Var2"="names"))

DF.pur$exp <- round((DF.pur$degree.tr * DF.pur$degree.oc) / sum(A)) #(k_i*k_j)/(L)
DF.pur$diff <- DF.pur$value - DF.pur$exp
DF.pur$sparse <- ifelse(DF.pur$diff>=0, DF.pur$value, 0)

isco_names <- unique(db_bachelor[,c("ISCO3", "ISCO3_ENG")])
isco_names$ISCO3 <- as.character(isco_names$ISCO3)
DF.pur <- left_join(DF.pur, isco_names, by=c("Var2"="ISCO3"))
colnames(DF.pur)[9] <- "Occupation"

DF.pur %>% select(Var1, Occupation, value, exp, diff) %>% arrange(-diff) %>% head(10)

###
#DF.pur$Var1 <- as.factor(DF.pur$Var1)
#c <- data.frame(as.numeric(DF.pur$Var1), DF.pur$Var1)
#colnames(c) <- c("pr_code", "program")
#c <- c %>% arrange(pr_code) %>% unique()

#DF.pur <- left_join(DF.pur, c, by=c("Var1"="program"))
#edges.HE.w <- DF.pur %>% select(pr_code, Var2, value)
#colnames(edges.HE.w) <- c("pr_code", "isco", "weight")
#write.csv2(edges.HE.w, "edges.w.csv", sep=";", row.names=F)
#write.csv2(c, "HE_codes.csv", sep=";", row.names=F)
```

##2.8. Weakest connections (Table5)

```{r, echo=F}
DF.pur %>% select(Var1, Occupation, value, exp, diff) %>% arrange(diff) %>% head(10)
```

#3. Analysis of degree distributions

##3.1. "Program set" of bipartite graph (Fig. 5)
```{r, echo=F}
data <- degree(g, v=V(g)[which(V(g)$type==FALSE)])
data <- data[data>0]
```

The initial distribution of data can be seen on figure below.

```{r, echo=F}
data.dist <- data.frame(k=0:max(data),p_k=degree_distribution(g, v=V(g)[which(V(g)$type==FALSE)]))
data.dist <- data.dist[data.dist$p_k>0,]
```

```{r distribution_plot_tr.w, fig.align="center", dpi=300, echo=F}
ggplot(data.dist) + geom_point(aes(x=k, y=p_k)) + theme_bw()
```

###Initial estimation

This estimation calcualate $K_{min}$, $\gamma$ and makes CDF and determine minimum $D$. With {poweRlaw} functions very easy to achive suggested steps 1-3.

```{r, echo=F}
m_pl <- displ$new(data)
est_pl <- estimate_xmin(m_pl)

est_pl$xmin #k_min
est_pl$pars #gamma
est_pl$gof #D
```

###Scanning whole range

```{r for_cicle_D_gamma_kmin.tr.w, fig.align="center", echo=F}
data.s <- unique(data)

d_est <- data.frame(K_min=sort(data.s)[1:(length(data.s)-2)], gamma=rep(0,length(data.s)-2), D=rep(0,length(data.s)-2))

for (i in d_est$K_min){
  d_est[which(d_est$K_min == i),2] <- estimate_xmin(m_pl, xmins = i)$pars
  d_est[which(d_est$K_min == i),3] <- estimate_xmin(m_pl, xmins = i)$gof
}

K.min_D.min <- d_est[which.min(d_est$D), 1]
```

```{r Kmin_vs_D_plot.tr.w, fig.align="center", dpi=300, echo=F}
ggplot(data=d_est, aes(x=K_min, y=D)) + geom_line() + theme_bw() + 
  geom_vline(xintercept=K.min_D.min, colour="red") + annotate("text", x=K.min_D.min, y=max(d_est$D)/3*2, label=K.min_D.min)
```

```{r kmin_vs_gamma_plot.tr.w, fig.align="center", dpi=300, echo=F}
ggplot(data=d_est, aes(x=K_min, y=gamma)) + geom_line() + theme_bw() + 
  geom_vline(xintercept=K.min_D.min, colour="red") + annotate("text", x=K.min_D.min, y=max(d_est$gamma)/3*2, label=K.min_D.min)
```

And the fitted power-law on CDF curve.

```{r powerlaw_figure_CDF.tr.w, fig.align="center", echo=F}
m_pl$setXmin(est_pl)
plot.data <- plot(m_pl, draw = F)
fit.data <- lines(m_pl, draw = F)
```

```{r PL_on_CDF.tr.w, fig.align="center", dpi=300, echo=F}
ggplot(plot.data) + geom_point(aes(x=log(x), y=log(y))) + labs(x="log(k)", y="log(CDF)") + theme_bw() + 
  geom_line(data=fit.data, aes(x=log(x), y=log(y)), colour="red")  
```

###Investigate goodness of fit

```{r powerlaw_estimations_by_bootstrapping.tr.w, message=F, warning=F, fig.align="center", dpi=300, echo=F}
bs_pl <- bootstrap_p(m_pl, no_of_sims=1000, threads=8, seed = 123)
#threads=core number of processor that used by function
#parallel::detectCores() determines how many cores in your computer

plot(bs_pl)
```

```{r bootstrap_figures.tr.w, warning=F, message=F, fig.align="center", echo=F}
df_bs_pl <- bs_pl$bootstraps
```

```{r frequency_gamma.tr.w, fig.align="center", message=F, warning=F, dpi=300, echo=F}
ggplot(data=df_bs_pl, aes(pars)) + geom_histogram() + labs(x="gamma", y="frequency") + theme_bw()
```

```{r frequency_kmin.tr.w, fig.align="center", message=F, warning=F, dpi=300, echo=F}
ggplot(data=df_bs_pl, aes(xmin)) + geom_histogram() + labs(x="K_min", y="frequency") + theme_bw()
```

```{r gamma_vs_kmin.tr.w, fig.align="center", dpi=300, echo=F}
gamma_D.min <- d_est[which.min(d_est$D), 2]

ggplot(data=df_bs_pl, aes(x=xmin, y=pars)) + labs(x="K_min", y="gamma") + theme_bw() + 
  geom_point(shape=21, colour="black", fill="red", size=0.5, stroke=2, 
             position = position_jitter(), alpha=0.6) +
  geom_vline(xintercept=K.min_D.min, colour="blue") +
  geom_hline(yintercept=gamma_D.min, colour="blue") +
  annotate("text", x=K.min_D.min, y=min(df_bs_pl$pars), label=K.min_D.min, col="blue") +
  annotate("text", x=min(df_bs_pl$xmin), y=gamma_D.min, label=round(gamma_D.min, digits=2), col="blue")
```

Initial estimated $\gamma$ and $K_{min}$ denoted with blue colour on the figure.

```{r D_real_D_synthetic.tr.w, fig.align="center", message=F, warning=F, dpi=300, echo=F}
D.min <- d_est[which.min(d_est$D), 3]

ggplot(data=df_bs_pl, aes(gof)) + geom_histogram() + labs(x="D", y="frequency") + geom_vline(xintercept=D.min, colour="red") + theme_bw()

bs_pl$p #p value
```

The $p$ value is `r bs_pl$p`. If $p$ value more than 1% means that null hypothesis cannot be rejected maybe it is a power-law distribution.


###Fitting real distribution

```{r saturation_cutoff.tr.w, warning=F, message=F, echo=F}
#generate kmin & kmax pairs
pairs <- as.data.frame(t(combn(sort(data.s), 2)))
pairs$D <- rep(0, length(pairs$V1))
pairs$gamma <- rep(0, length(pairs$V1))

#scan D for all kmin-kmax pairs
for (i in 1:length(pairs$D)){
  m_pl$setXmin(pairs[i,1])
  pairs[i,3]<- estimate_xmin(m_pl, xmin = pairs[i,1], xmax = pairs[i,2], distance = "ks")$gof
  pairs[i,4]<- estimate_xmin(m_pl, xmin = pairs[i,1], xmax = pairs[i,2], distance = "ks")$pars
}

bs_pl_sat_cut <- bootstrap_p(m_pl, xmins = pairs[which.min(pairs$D), 1], xmax = pairs[which.min(pairs$D), 2], no_of_sims = 1000, threads = 8)

#in this range
pairs[which.min(pairs$D), 3] -> D.tr.w
bs_pl_sat_cut$p -> p.tr.w

pairs[which.min(pairs$D), 1] -> k_sat.tr.w
pairs[which.min(pairs$D), 2] -> k_cut.tr.w
pairs[which.min(pairs$D), 4] -> gamma.tr.w
```

* $k_{sat}$ = `r pairs[which.min(pairs$D), 1]`
* $k_{cut}$ = `r pairs[which.min(pairs$D), 2]`
* _D_ = `r pairs[which.min(pairs$D), 3]`
* $\gamma$ = `r pairs[which.min(pairs$D), 4]`
* _p_ = `r bs_pl_sat_cut$p` (by bootstratpping)

```{r compare_different_distributions.tr.w, echo=F}
#powerlaw
m_pl = displ$new(data)
est_pl <- estimate_xmin(m_pl, xmins = k_sat.tr.w, xmax = k_cut.tr.w, pars= gamma.tr.w, distance = "ks")
m_pl$setXmin(est_pl)

#lognormal
m_ln = dislnorm$new(data)
est_ln <- estimate_xmin(m_ln)
m_ln$setXmin(est_ln)

#exponential
m_exp = disexp$new(data)
est_exp <- estimate_xmin(m_exp)
m_exp$setXmin(est_exp)

#poisson
m_poi = dispois$new(data)
est_poi <- estimate_xmin(m_poi)
m_poi$setXmin(est_poi)
```

This figure compares different distributions. (red: power-law, green: lognormal, blue: Poisson, magenta: exponential)

```{r compare_different_distributions_figure.tr.w, fig.align="center", dpi=300, echo=F}
plot(m_pl)
lines(m_pl, col="red")
lines(m_ln, col="green")
lines(m_poi, col="blue")
lines(m_exp, col="magenta")
```

```{r powerlaw_figure_CDF.tr, fig.align="center", echo=F}
m_pl$setXmin(est_pl)
plot.data <- plot(m_pl, draw = F)
fit.data <- lines(m_pl, draw = F)
fit.data.ln <- lines(m_ln, draw=F)
fit.data.poi <- lines(m_poi, draw=F)
fit.data.exp <- lines(m_exp, draw=F)
```

```{r PL_on_CDF.tr2, fig.align="center", dpi=300, echo=F}
ggplot(plot.data) + 
  geom_point(aes(x=log(x), y=log(y))) + 
  labs(x="log(k)", y=bquote(log ~p[k])) + 
  theme_bw() + 
  geom_line(data=fit.data[1:74,], aes(x=log(x), y=log(y), colour="Power-law"), size=0.8) +
  geom_line(data=fit.data.ln, aes(x=log(x), y=log(y), colour="Log-normal"), size=0.2) +
  geom_line(data=fit.data.poi[1:45, ], aes(x=log(x), y=log(y), colour="Poisson"), size=0.2) +
  geom_line(data=fit.data.exp[1:90,], aes(x=log(x), y=log(y), colour="Exponential"), size=0.2) +
  geom_vline(aes(xintercept=log(31)), color = 'red', linetype = 'dashed') +
  geom_vline(aes(xintercept=log(367)), color = 'red', linetype = 'dashed') +
  annotate("text", x = 3.3, y = -3, label="k[sat] == 31 ", color="red", angle=90, parse=T) +
  annotate("text", x = 5.7, y = -1, label="k[cut] == 367", color="red", angle=90, parse=T) +
  annotate("text", x = 4.6, y = -2.8, label="gamma == 2.00", color="red", parse=T) +
  scale_colour_manual("", 
                      breaks = c("Power-law", "Log-normal", "Poisson", "Exponential"),
                      values = c("magenta", "green", "blue", "red"))

#ggsave("Fig8_v2.pdf", width = 19, height=10, units="cm")
```

Compare lognormal and powerlaw distribution with Vuong's test

```{r compare_pl_ln, fig.align="center", echo=F}
m_ln$setXmin(31)

comp <- compare_distributions(m_pl, m_ln)
comp$p_two_sided
```

##3.2. "Occupation set" of bigraph (Fig. 6)
```{r, echo=F}
data <- degree(g, v=V(g)[which(V(g)$type==TRUE)])
data <- data[data>0]
```

The initial distribution of data can be seen on figure below.

```{r, echo=F}
data.dist <- data.frame(k=0:max(data),p_k=degree_distribution(g, v=V(g)[which(V(g)$type==TRUE)]))
data.dist <- data.dist[data.dist$p_k>0,]
```

```{r distribution_plot.oc.w, fig.align="center", dpi=300, echo=F}
ggplot(data.dist) + geom_point(aes(x=k, y=p_k)) + theme_bw()
```

It is very similar to power-law distribution but let it see with {powerLaw}.

###Initial estimation

This estimation calcualate $K_{min}$, $\gamma$ and makes CDF and determine minimum $D$. With {poweRlaw} functions very easy to achive suggested steps 1-3.

```{r, echo=F}
m_pl <- displ$new(data)
est_pl <- estimate_xmin(m_pl)

est_pl$xmin #k_min
est_pl$pars #gamma
est_pl$gof #D
```

###Scanning whole range

```{r for_cicle_D_gamma_kmin.oc.w, fig.align="center", echo=F}
data.s <- unique(data)

d_est <- data.frame(K_min=sort(data.s)[1:(length(data.s)-2)], gamma=rep(0,length(data.s)-2), D=rep(0,length(data.s)-2))

for (i in d_est$K_min){
  d_est[which(d_est$K_min == i),2] <- estimate_xmin(m_pl, xmins = i)$pars
  d_est[which(d_est$K_min == i),3] <- estimate_xmin(m_pl, xmins = i)$gof
}

K.min_D.min <- d_est[which.min(d_est$D), 1]
```

```{r Kmin_vs_D_plot.oc.w, fig.align="center", dpi=300, echo=F}
ggplot(data=d_est, aes(x=K_min, y=D)) + geom_line() + theme_bw() + 
  geom_vline(xintercept=K.min_D.min, colour="red") + annotate("text", x=K.min_D.min, y=max(d_est$D)/3*2, label=K.min_D.min)
```

```{r kmin_vs_gamma_plot.oc.w, fig.align="center", dpi=300, echo=F}
ggplot(data=d_est, aes(x=K_min, y=gamma)) + geom_line() + theme_bw() + 
  geom_vline(xintercept=K.min_D.min, colour="red") + annotate("text", x=K.min_D.min, y=max(d_est$gamma)/3*2, label=K.min_D.min)
```

And the fitted power-law on CDF curve.

```{r powerlaw_figure_CDF.oc.w, fig.align="center", echo=F}
m_pl$setXmin(est_pl)
plot.data <- plot(m_pl, draw = F)
fit.data <- lines(m_pl, draw = F)
```

```{r PL_on_CDF.oc.w, fig.align="center", dpi=300, echo=F}
ggplot(plot.data) + geom_point(aes(x=log(x), y=log(y))) + labs(x="log(k)", y="log(CDF)") + theme_bw() + 
  geom_line(data=fit.data, aes(x=log(x), y=log(y)), colour="red")  
```

###Investigate goodness of fit

```{r powerlaw_estimations_by_bootstrapping.oc.w, message=F, warning=F, fig.align="center", dpi=300, echo=F}
bs_pl <- bootstrap_p(m_pl, no_of_sims=1000, threads=8, seed = 123)
#threads=core number of processor that used by function
#parallel::detectCores() determines how many cores in your computer

plot(bs_pl)
```

```{r bootstrap_figures.oc.w, warning=F, message=F, fig.align="center", echo=F}
df_bs_pl <- bs_pl$bootstraps
```

```{r frequency_gamma.oc.w, fig.align="center", message=F, warning=F, dpi=300, echo=F}
ggplot(data=df_bs_pl, aes(pars)) + geom_histogram() + labs(x="gamma", y="frequency") + theme_bw()
```

```{r frequency_kmin.oc.w, fig.align="center", message=F, warning=F, dpi=300, echo=F}
ggplot(data=df_bs_pl, aes(xmin)) + geom_histogram() + labs(x="K_min", y="frequency") + theme_bw()
```

```{r gamma_vs_kmin.oc.w, fig.align="center", dpi=300, echo=F}
gamma_D.min <- d_est[which.min(d_est$D), 2]

ggplot(data=df_bs_pl, aes(x=xmin, y=pars)) + labs(x="K_min", y="gamma") + theme_bw() + 
  geom_point(shape=21, colour="black", fill="red", size=0.5, stroke=2, 
             position = position_jitter(), alpha=0.6) +
  geom_vline(xintercept=K.min_D.min, colour="blue") +
  geom_hline(yintercept=gamma_D.min, colour="blue") +
  annotate("text", x=K.min_D.min, y=min(df_bs_pl$pars), label=K.min_D.min, col="blue") +
  annotate("text", x=min(df_bs_pl$xmin), y=gamma_D.min, label=round(gamma_D.min, digits=2), col="blue")
```

Initial estimated $\gamma$ and $K_{min}$ denoted with blue colour on the figure.

```{r D_real_D_synthetic.oc.w, fig.align="center", message=F, warning=F, dpi=300, echo=F}
D.min <- d_est[which.min(d_est$D), 3]

ggplot(data=df_bs_pl, aes(gof)) + geom_histogram() + labs(x="D", y="frequency") + geom_vline(xintercept=D.min, colour="red") + theme_bw()

bs_pl$p #p value
```

The $p$ value is `r bs_pl$p`. If $p$ value more than 1% means that null hypothesis cannot be rejected maybe it is a power-law distribution.


###Fitting real distribution

```{r saturation_cutoff.oc.w, warning=F, message=F, echo=F}
#generate kmin & kmax pairs
pairs <- as.data.frame(t(combn(sort(data.s), 2)))
pairs$D <- rep(0, length(pairs$V1))
pairs$gamma <- rep(0, length(pairs$V1))

#scan D for all kmin-kmax pairs
for (i in 1:length(pairs$D)){
  m_pl$setXmin(pairs[i,1])
  pairs[i,3]<- estimate_xmin(m_pl, xmin = pairs[i,1], xmax = pairs[i,2], distance = "ks")$gof
  pairs[i,4]<- estimate_xmin(m_pl, xmin = pairs[i,1], xmax = pairs[i,2], distance = "ks")$pars
}

bs_pl_sat_cut <- bootstrap_p(m_pl, xmins = pairs[which.min(pairs$D), 1], xmax = pairs[which.min(pairs$D), 2], no_of_sims = 1000, threads = 8)

#in this range
pairs[which.min(pairs$D), 3] -> D.oc.w
pairs[which.min(pairs$D), 4] -> gamma.oc.w
bs_pl_sat_cut$p -> p.oc.w

pairs[which.min(pairs$D), 1] -> k_sat.oc.w
pairs[which.min(pairs$D), 2] -> k_cut.oc.w
pairs[which.min(pairs$D), 4] -> gamma.oc.w
```

* $k_{sat}$ = `r pairs[which.min(pairs$D), 1]`
* $k_{cut}$ = `r pairs[which.min(pairs$D), 2]`
* _D_ = `r pairs[which.min(pairs$D), 3]`
* $\gamma$ = `r pairs[which.min(pairs$D), 4]`
* _p_ = `r bs_pl_sat_cut$p` (by bootstratpping)

```{r compare_different_distributions.oc.w, echo=F}
#powerlaw
m_pl = displ$new(data)
est_pl <- estimate_xmin(m_pl, xmins = k_sat.oc.w, xmax = k_cut.oc.w, pars = gamma.oc.w, distance = "ks")
m_pl$setXmin(est_pl)

#lognormal
m_ln = dislnorm$new(data)
est_ln <- estimate_xmin(m_ln)
m_ln$setXmin(est_ln)

#exponential
m_exp = disexp$new(data)
est_exp <- estimate_xmin(m_exp)
m_exp$setXmin(est_exp)

#poisson
m_poi = dispois$new(data)
est_poi <- estimate_xmin(m_poi)
m_poi$setXmin(est_poi)
```

```{r powerlaw_figure_CDF.oc.w2, fig.align="center", echo=F}
m_pl$setXmin(est_pl)
plot.data <- plot(m_pl, draw = F)
fit.data <- lines(m_pl, draw = F)
```

```{r PL_on_CDF.oc2, fig.align="center", dpi=300, echo=F}
ggplot(plot.data) + 
  geom_point(aes(x=log(x), y=log(y))) + 
  labs(x="log(k)", y=bquote(log ~p[k])) + 
  theme_bw() + 
  geom_line(data=fit.data[1:83,], aes(x=log(x), y=log(y)), colour="red", size=0.8) +
  geom_vline(aes(xintercept=log(32)), color = 'red', linetype = 'dashed') +
  geom_vline(aes(xintercept=log(371)), color = 'red', linetype = 'dashed') +
  annotate("text", x = 3.3, y = -3, label="k[sat] == 32 ", color="red", angle=90, parse=T) +
  annotate("text", x = 5.7, y = -1, label="k[cut] == 371", color="red", angle=90, parse=T) +
  annotate("text", x = 4.6, y = -2.8, label="gamma == 2.00", color="red", parse=T)

#ggsave("Fig7.eps", width = 19, units="cm")
```


This figure compares different distributions. (red: power-law, green: lognormal, blue: Poisson, magenta: exponential)

```{r compare_different_distributions_figure.oc.w, fig.align="center", dpi=300, echo=F}
plot(m_pl)
lines(m_pl, col="red")
lines(m_ln, col="green")
lines(m_poi, col="blue")
lines(m_exp, col="magenta")
```

```{r powerlaw_figure_CDF.oc, fig.align="center", echo=F}
m_pl$setXmin(est_pl)
plot.data <- plot(m_pl, draw = F)
fit.data <- lines(m_pl, draw = F)
fit.data.ln <- lines(m_ln, draw=F)
fit.data.poi <- lines(m_poi, draw=F)
fit.data.exp <- lines(m_exp, draw=F)
```

```{r PL_on_CDF.tr2B, fig.align="center", dpi=300, echo=F}
ggplot(plot.data) + 
  geom_point(aes(x=log(x), y=log(y))) + 
  labs(x="log(k)", y=bquote(log ~p[k])) + 
  theme_bw() + 
  geom_line(data=fit.data[1:83,], aes(x=log(x), y=log(y), colour="Power-law"), size=0.8) +
  geom_line(data=fit.data.ln, aes(x=log(x), y=log(y), colour="Log-normal"), size=0.2) +
  geom_line(data=fit.data.poi[1:50, ], aes(x=log(x), y=log(y), colour="Poisson"), size=0.2) +
  geom_line(data=fit.data.exp[1:90,], aes(x=log(x), y=log(y), colour="Exponential"), size=0.2) +
  geom_vline(aes(xintercept=log(32)), color = 'red', linetype = 'dashed') +
  geom_vline(aes(xintercept=log(371)), color = 'red', linetype = 'dashed') +
  annotate("text", x = 3.3, y = -3, label="k[sat] == 32 ", color="red", angle=90, parse=T) +
  annotate("text", x = 5.7, y = -1, label="k[cut] == 371", color="red", angle=90, parse=T) +
  annotate("text", x = 4.6, y = -2.8, label="gamma == 2.00", color="red", parse=T) +
  scale_colour_manual("", 
                      breaks = c("Power-law", "Log-normal", "Poisson", "Exponential"),
                      values = c("magenta", "green", "blue", "red"))

#ggsave("Fig7_v2.pdf", width = 19, height=10, units="cm")
```

Compare lognormal and powerlaw distribution with Vuong's test

```{r compare_pl_ln2, fig.align="center", echo=F}
m_ln$setXmin(32)

comp <- compare_distributions(m_pl, m_ln)
comp$p_two_sided
```

#4. Node measures

##4.1. Centralities
```{r, echo=F}
g.pr <- data.frame(nodes=rep(0, 223))
g.pr$nodes <- V(g)$name
#rownames(g.pr) <- g.pr$nodes
g.pr$occ <- 0
g.pr$occ[111:223] <- 1
g.pr$degree.weighted <- degree(g)
g.pr$degree <- degree(g.sim)
g.pr$betweenness.w <- betweenness(g)
g.pr$betweenness <- betweenness(g.sim)
g.pr$eigen.centr.w <- evcent(g)$vector
g.pr$eigen.centr <- evcent(g.sim)$vector
g.pr$power.centr.w <- power_centrality(g)
g.pr$power.centr <- power_centrality(g.sim)

ccBip <- function(g) {
  if (! "name" %in% list.vertex.attributes(g)) {
    V(g)$name <- seq_len(vcount(g))
  }
  neib <- get.adjlist(g)
  names(neib) <- V(g)$name
  proj <- bipartite.projection(g)
  lapply(proj, function(x) {
    el <- get.edgelist(x)
    sapply(V(x)$name, function(v) {
      subs <- el[,1]==v | el[,2]==v
      f <- function(un, vn) length(union(un, vn))
      vals <- E(x)[subs]$weight / unlist(mapply(f, neib[el[subs,1]], neib[el[subs,2]]))
      mean(vals)
    })
  })
}

a <- ccBip(g)
g.pr$transitivity.w <- c(a$proj1, a$proj2)

a <- ccBip(g.sim)
g.pr$transitivity <- c(a$proj1, a$proj2)

g.pr$closeness.w <- closeness(g)
g.pr$closeness <- closeness(g.sim)

g.pr$pagerank.w <- page.rank(g)$vector
g.pr$pagerank <- page.rank(g)$vector

g.proj <- bipartite.projection(g)
g.pr$knn.w <- c(knn(g.proj$proj1)$knn, knn(g.proj$proj2)$knn)

head(g.pr)
```

##4.2. Distance distribution
```{r, echo=F}
mean_distance(g)
x <- distances(g)

y <- data.frame(min(x):max(x), sapply(min(x):max(x), function(k) length(which(x==k)))/sum(x))
colnames(y) <- c("d", "p_d")
res <- nls( p_d ~ k*exp(-1/2*(d-mu)^2/sigma^2), start=c(mu=2.5,sigma=1.5,k=1) , data = y)
v <- summary(res)$parameters[,"Estimate"]
fun <- function(d) v[3]*exp(-1/2*(d-v[1])^2/v[2]^2)

ggplot(y, aes(x=d, y=p_d)) + geom_point() + 
  stat_function(fun = fun, color = "red") +
  theme_bw() + labs(title="Distance distribution of graph")
```

fitted equation:
function(d) $k*exp(-1/2*(d-mu)^2/sigma^2)$

k = `r v[3]`
mu = `r v[1]`
sigma = `r v[2]`

The variance of distances is sigma=`r v[2]`, indicating that most path legths are in a close vicinity of mean d. These are manifestations of the small world property. [Barabasi: Network science, 2015]

##4.3. Farthest nodes
```{r, echo=F}
q <- which(x==5, arr.ind = TRUE)[1:2,]
paste(rownames(x)[q[1,1]], "-", colnames(x)[q[1,2]])
paste(rownames(x)[q[2,1]], "-", colnames(x)[q[2,2]])
```


#5. Clustering methods

##5.1. Create purified graph
Purified with configuration model (alpha=0.5)

```{r sparsify_by_configuration_model_10, echo=F, warning=F, message=F, echo=F}
DF.pur <- melt(A)
DF.pur <- DF.pur[DF.pur$value!=0,]
DF.pur$Var2 <- as.factor(DF.pur$Var2)

degree.tr <- data.frame(rownames(A),rowSums(A))
names(degree.tr) <- c("names", "degree.tr")
degree.oc <- data.frame(colnames(A),colSums(A))
names(degree.oc) <- c("names", "degree.oc")

DF.pur <- left_join(DF.pur, degree.tr, by=c("Var1"="names"))
DF.pur <- left_join(DF.pur, degree.oc, by=c("Var2"="names"))

DF.pur$exp <- round((DF.pur$degree.tr * DF.pur$degree.oc * 0.5) / sum(A)) #(k_i*k_j)/(L)
DF.pur$diff <- DF.pur$value - DF.pur$exp
DF.pur$sparse <- ifelse(DF.pur$diff>=0, DF.pur$value, 0)

A.pur <- acast(DF.pur, Var1 ~ Var2, value.var = "sparse")
A.pur[is.na(A.pur)] <- 0

g.pur <- graph.incidence(A.pur, directed=F, multiple = T)

g.pur.sim <- simplify(g.pur) #unweighted graph
A.pur.sim <- get.incidence(g.pur.sim)
```

Number of connection in original graph and purified graph:
* before: L = `r sum(A)`
* after: L_pur = `r sum(A.pur)`


##5.2. Louvain (Fig. 8)

```{r, echo=F, warning=F, message=F}
lou <- cluster_louvain(g.pur)
x.lou <- data.frame(lou$names,lou$membership)

longData<-melt(A)
longData<-longData[longData$value!=0,]
longData <- left_join(longData, x.lou, by=c("Var1"="lou.names"))
colnames(longData)[4] <- "Var1_clust"
longData$Var2 <- as.factor(longData$Var2)
longData <- left_join(longData, x.lou, by=c("Var2"="lou.names"))
colnames(longData)[5] <- "Var2_clust"
longData$col <- ifelse(longData$Var1_clust==longData$Var2_clust, longData$Var1_clust, 0)

longData$Var1 <- factor(longData$Var1, levels=unique(arrange(longData, Var1_clust)[,1]))
longData$Var2 <- factor(longData$Var2, levels=unique(arrange(longData, Var2_clust)[,2]))
longData$col <- factor(longData$col)

#color palette for axis
axis.y.colour <- (longData %>% select(Var1, Var1_clust) %>% unique %>% arrange(Var1_clust) %>% select(Var1_clust))[,1] %>% plyr::mapvalues(from=c(1:10), to=c("#B40404", "#0B6121", "#40FF00", "#FA58D0", "#000000", "#FFBF00", "#997300", "#077292", "#58D3F7", "#336699"))

axis.x.colour <- (longData %>% select(Var2, Var2_clust) %>% unique %>% arrange(Var2_clust) %>% select(Var2_clust))[,1] %>% plyr::mapvalues(from=c(1:10), to=c("#B40404", "#0B6121", "#40FF00", "#FA58D0", "#000000", "#FFBF00", "#997300", "#077292", "#58D3F7", "#336699"))
```

```{r A.pur_Louvain_figure, fig.align="center", echo=F, fig.height=6.5, message=F, warning=F}
ggplot(longData, aes(x = Var2, y = Var1)) + 
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low="grey60", high="red") +
  labs(x="", y="") +
  theme_bw() + theme(axis.text.x=element_text(size=4, angle=90, vjust=0.4),
                     axis.text.y=element_text(size=4),
                     legend.text=element_text(size=8),
                     legend.title=element_text(size=8)) +
  theme(axis.text.y=element_text(colour=axis.y.colour)) +
  theme(axis.text.x=element_text(colour=axis.x.colour)) +
  annotate("segment", x = 30.5, xend = 30.5, y = 0, yend = 110.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 52.5, xend = 52.5, y = 0, yend = 110.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 72.5, xend = 72.5, y = 0, yend = 110.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 88.5, xend = 88.5, y = 0, yend = 110.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 0, xend = 113,5, y = 30.5, yend = 30.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 0, xend = 113.5, y = 49.5, yend = 49.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 0, xend = 113.5, y = 72.5, yend = 72.5, colour = "blue", size = 0.2) +
  annotate("segment", x = 0, xend = 113.5, y = 87.5, yend = 87.5, colour = "blue", size = 0.2) +
  annotate("text", label="A", x=25, y=25, color="#B40404", size=6 , fontface="bold") +
  annotate("text", label="B", x=50, y=46, color="#0B6121", size=6 , fontface="bold") +
  annotate("text", label="C", x=65, y=65, color="#40FF00", size=6 , fontface="bold") +
  annotate("text", label="D", x=83, y=85, color="#FA58D0", size=6 , fontface="bold") +
  annotate("text", label="E", x=110, y=107, color="#000000", size=6 , fontface="bold")

#ggsave("Fig8.pdf", width = 22.23, units="cm")
```


###Table 6.

```{r Aij-Pij_Louvain, echo=F, warning=F, message=F}
longData2 <- melt(A)
longData2$Var2 <- as.character(longData2$Var2)
colnames(longData2)[3] <- "Aij"
#longData2 <- longData2[longData2$Aij>0,]

degree.tr <- data.frame(rownames(A),rowSums(A))
names(degree.tr) <- c("names", "degree.tr")
degree.oc <- data.frame(colnames(A),colSums(A))
names(degree.oc) <- c("names", "degree.oc")

longData2 <- left_join(longData2, degree.tr, by=c("Var1"="names"))
longData2 <- left_join(longData2, degree.oc, by=c("Var2"="names"))

longData2$Pij <- (longData2$degree.tr * longData2$degree.oc) / sum(A) #(k_i*k_j)/(L)

longData2$Bij <- longData2$Aij - longData2$Pij

longData2 <- left_join(longData2, x.lou, by=c("Var1"="lou.names"))
colnames(longData2)[8] <- "Var1_clust"
longData2$Var2 <- as.factor(longData2$Var2)
longData2 <- left_join(longData2, x.lou, by=c("Var2"="lou.names"))
colnames(longData2)[9] <- "Var2_clust"

aggdata2 <-aggregate(longData2$Aij, by=list(longData2$Var1_clust, longData2$Var2_clust),FUN=sum)
Aij <- acast(aggdata2, Group.1 ~ Group.2, value.var = "x")
Aij[is.na(Aij)] <- 0
Aij <- Aij[nrow(Aij):1,]

aggdata <-aggregate(longData2$Pij, by=list(longData2$Var1_clust, longData2$Var2_clust),FUN=sum)
Pij <- acast(aggdata, Group.1 ~ Group.2, value.var = "x")
Pij[is.na(Pij)] <- 0
Pij <- Pij[nrow(Pij):1,]

round(Aij / Pij,3)

```

###Germanistics
An expample
```{r, echo=F}
ger <- db_bachelor %>% filter(Pr_ENG_bachelor=="Germanistics")
prop.table(table(ger$ISCO3_ENG))
```


##5.3. BRIM - Barber algorithm (Fig. 9)


```{r, echo=F}
mod <- findModules(t(A.pur), iter = 100, sparse = F)

A.x <- mod$M
```

This algorithm has a bootstrapping step. That is why there is no two exactly same figure. But modules are the same. Seed was not set.

```{r, echo=F}
plotModules(mod)
```

#6. Multi-resolution method

##6.1. Reamain L after purification (Fig. 7)

```{r}
L <- rep(0, 101)

for (i in 0:100){
j <- i/10
DF.pur <- melt(A)
DF.pur <- DF.pur[DF.pur$value!=0,]
DF.pur$Var2 <- as.factor(DF.pur$Var2)

degree.tr <- data.frame(rownames(A),rowSums(A))
names(degree.tr) <- c("names", "degree.tr")
degree.oc <- data.frame(colnames(A),colSums(A))
names(degree.oc) <- c("names", "degree.oc")

DF.pur <- left_join(DF.pur, degree.tr, by=c("Var1"="names"))
DF.pur <- left_join(DF.pur, degree.oc, by=c("Var2"="names"))

DF.pur$exp <- round((DF.pur$degree.tr * DF.pur$degree.oc * j) / sum(A)) #(k_i*k_j)/(L)
DF.pur$diff <- DF.pur$value - DF.pur$exp
DF.pur$sparse <- ifelse(DF.pur$diff>=0, DF.pur$value, 0)
L[i+1] <- sum(DF.pur$sparse)
}

L.df <- data.frame(alpha=seq(0,10, by=0.1), L=L)
L.df$L <- L.df$L/7402
```

```{r}
ggplot(L.df) + geom_point(aes(x=alpha, y=L)) + 
  ylab(expression(L[p]/L)) + xlab(expression(alpha)) + 
  scale_x_continuous(breaks=seq(0,10,by=1)) +
  theme_bw()

#ggsave("Fig_Lp_vs_alpha.pdf", height=4.5, width=7)
```

##6.2. Multi-resolution method with Louvain: training programs

###Scanning gamma (Fig. 10)

```{r}
Q.var <- rep(0, 101)
clust <- matrix(0, nrow=223, ncol=101) #223 node, 101 gamma value
L <- rep(0, 101)
connections <- rep(0, 101)

for (i in 0:100){
j <- i/10
DF.pur <- melt(A)
DF.pur <- DF.pur[DF.pur$value!=0,]
DF.pur$Var2 <- as.factor(DF.pur$Var2)

degree.tr <- data.frame(rownames(A),rowSums(A))
names(degree.tr) <- c("names", "degree.tr")
degree.oc <- data.frame(colnames(A),colSums(A))
names(degree.oc) <- c("names", "degree.oc")

DF.pur <- left_join(DF.pur, degree.tr, by=c("Var1"="names"))
DF.pur <- left_join(DF.pur, degree.oc, by=c("Var2"="names"))

DF.pur$exp <- round((DF.pur$degree.tr * DF.pur$degree.oc * j) / sum(A)) #(k_i*k_j)/(L)
DF.pur$diff <- DF.pur$value - DF.pur$exp
DF.pur$sparse <- ifelse(DF.pur$diff>=0, DF.pur$value, 0)
L[i+1] <- sum(DF.pur$sparse)
connections[i+1] <- 2054-sum(DF.pur$sparse==0)

A.pur <- acast(DF.pur, Var1 ~ Var2, value.var = "sparse")
A.pur[is.na(A.pur)] <- 0

g.pur <- graph.incidence(A.pur, directed=F, weighted = T)

lou <- cluster_louvain(g.pur)

clust[,i+1] <- lou$membership
Q.var[i+1] <- modularity(lou)
}

rownames(clust) <- lou$names
colnames(clust) <- seq(0, 10, 0.1)
```

###Number of clusters

```{r}
C <- sapply(1:ncol(clust), function(x) max(clust[,x]))
C <- data.frame(seq(0,10,0.1), C)
colnames(C)[1] <- "gamma"
```

```{r}
#ggplot(C, aes(x=gamma, y=C)) + geom_point() + theme_bw()
ggplot(C[1:50,], aes(x=gamma, y=C)) + geom_point(size=1.2) + theme_bw() +
  annotate("segment", x = 1.8, xend = 1.2, y = 5, yend = 5, colour="blue", size=1, arrow=arrow()) + 
  annotate("segment", x = 4.2, xend = 3.6, y = 10, yend = 10, colour="blue", size=1, arrow=arrow()) +
  labs(y="Number of clusters", x="alpha")

#ggsave("cikkbe_Fig_C_vs_gamma.pdf", height = 14, width=16, units="cm")
```

###Number of weights

```{r}
L <- data.frame(seq(0,10,0.1), L)
colnames(L)[1] <- "gamma"
```

```{r}
ggplot(L, aes(x=gamma, y=L)) + geom_point() + theme_bw()
ggplot(L[1:70,], aes(x=gamma, y=L)) + geom_point() + theme_bw()
```

###Number of links

```{r}
connections <- data.frame(seq(0,10,0.1), connections)
colnames(connections)[1] <- "gamma"
```

```{r}
ggplot(connections, aes(x=gamma, y=connections)) + geom_point() + theme_bw()
ggplot(connections[1:70,], aes(x=gamma, y=connections)) + geom_point() + theme_bw()
```

###Similarity of nodes

```{r}
S <- matrix(0, nrow=223, ncol=223)
rownames(S) <- rownames(clust)
colnames(S) <- rownames(clust)
```

```{r}
res1 <- 1
res2 <- 11
for (i in 1:223){
  for (j in 1:223){
    S[i,j] <- sum(clust[i,res1:res2]-clust[j,res1:res2]==0)
    S[j,i] <- S[i,j]
  }
}

S.pr <- S[1:110, 1:110]
S.pr <- S.pr/(res2-res1+1)
```

```{r}
longData<-melt(S.pr)
longData<-longData[longData$value!=0,]

#o <- seriate(S.pr, method = "BEA_TSP")
#longData$Var1 <- factor(longData$Var1, levels=names(unlist(o[[1]][])))
#longData$Var2 <- factor(longData$Var2, levels=names(unlist(o[[1]][])))

#cl <- data.frame(names(unlist(o[[1]][])))

ord <- read.csv("ordering.csv")

#this ordering was saved for repeatability

longData$Var1 <- factor(longData$Var1, levels=ord[,2])
longData$Var2 <- factor(longData$Var2, levels=ord[,2])

cl <- data.frame(ord[,2])

colnames(cl)[1] <- "programs"

clust2 <- data.frame(rownames(clust), clust[,1])
rownames(clust2) <- 1:223
colnames(clust2) <- c("programs", "clusters")

cl <- left_join(cl, clust2, by="programs")

#color palette for axis
axis.x.colour <- (cl[,2] %>% plyr::mapvalues(from=c(1:10), to=c("#B40404", "#e68a00", "#0B6121", "#000099", "#0099cc", "#00cc99", "#6600cc", "#e600e6", "#999900", "#7094db")))

#ordering <- names(unlist(o[[1]][]))
#write.csv(ordering, "ordering.csv")
```

```{r}
ggplot(longData, aes(x = Var2, y = Var1)) + 
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low="grey60", high="red") +
  labs(x="", y="", title="") +
  theme_bw() + 
  theme(axis.text.x=element_text(size=5, angle=90, vjust=0.2, hjust=1),
                     axis.text.y=element_text(size=5),
                     legend.text=element_text(size=8),
                     legend.title=element_text(size=8)) +
  theme(axis.text.x=element_text(colour=axis.x.colour)) +
  theme(axis.text.y=element_text(colour=axis.x.colour)) +
  annotate("segment", x = 23.5, xend = 23.5, y = 0, yend = 110.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 42.5, xend = 42.5, y = 0, yend = 110.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 65.5, xend = 65.5, y = 0, yend = 110.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 95.5, xend = 95.5, y = 0, yend = 110.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 110.5, y = 23.5, yend = 23.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 110.5, y = 42.5, yend = 42.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 110.5, y = 65.5, yend = 65.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 110.5, y = 95.5, yend = 95.5, colour = "blue", size = 0.5)


#ggsave("cikkbe_Fig_2.9-3.4.pdf", height = 22, width=23, units="cm")
```

###Programs in clusters table (Fig. 11)

```{r}
table(clust[,30], clust[,1])

table(clust[1:110,30], clust[1:110,1]) #programs
table(clust[111:223,30], clust[111:223,1]) #occuptions

clu <- data.frame(
  name=rownames(clust),
  gamma0=clust[,1],
  gamma2.9=clust[,30])

colnames(degree.oc) <- colnames(degree.tr)
degree <- rbind(degree.tr, degree.oc)

clu <- left_join(clu, degree, by=c("name"="names"))

clu15 <- clu[clu$degree.tr>15,]
```


```{r}
ggplot(clu[clu$degree.tr>15,]) + geom_point(aes(x=gamma2.9, y=gamma0), color="red") + 
  geom_text_repel(aes(x=gamma2.9, y=gamma0, label=name), size=3) + 
  scale_x_discrete(limits=1:10) + 
  scale_y_discrete(limits=1:5) + 
  labs(x="alpha=2.9", y="alpha=0") + 
  theme_bw()

#ggsave("Fig_clusters.pdf", height = 22, width=42, units="cm")

```




##6.3. Multi-resolution method with Louvain: occupations

###Scanning gamma

```{r}
Q.var <- rep(0, 101)
clust <- matrix(0, nrow=223, ncol=101) #223 node, 101 gamma value
L <- rep(0, 101)
connections <- rep(0, 101)

for (i in 0:100){
j <- i/10
DF.pur <- melt(A)
DF.pur <- DF.pur[DF.pur$value!=0,]
DF.pur$Var2 <- as.factor(DF.pur$Var2)

degree.tr <- data.frame(rownames(A),rowSums(A))
names(degree.tr) <- c("names", "degree.tr")
degree.oc <- data.frame(colnames(A),colSums(A))
names(degree.oc) <- c("names", "degree.oc")

DF.pur <- left_join(DF.pur, degree.tr, by=c("Var1"="names"))
DF.pur <- left_join(DF.pur, degree.oc, by=c("Var2"="names"))

DF.pur$exp <- round((DF.pur$degree.tr * DF.pur$degree.oc * j) / sum(A)) #(k_i*k_j)/(L)
DF.pur$diff <- DF.pur$value - DF.pur$exp
DF.pur$sparse <- ifelse(DF.pur$diff>=0, DF.pur$value, 0)
L[i+1] <- sum(DF.pur$sparse)
connections[i+1] <- 2054-sum(DF.pur$sparse==0)

A.pur <- acast(DF.pur, Var1 ~ Var2, value.var = "sparse")
A.pur[is.na(A.pur)] <- 0

g.pur <- graph.incidence(A.pur, directed=F, weighted = T)

lou <- cluster_louvain(g.pur)

clust[,i+1] <- lou$membership
Q.var[i+1] <- modularity(lou)
}

rownames(clust) <- lou$names
colnames(clust) <- seq(0, 10, 0.1)
```


###Similarity of nodes

```{r}
S <- matrix(0, nrow=223, ncol=223)
rownames(S) <- rownames(clust)
colnames(S) <- rownames(clust)
```

```{r}
res1 <- 30
res2 <- 35
for (i in 1:223){
  for (j in 1:223){
    S[i,j] <- sum(clust[i,res1:res2]-clust[j,res1:res2]==0)
    S[j,i] <- S[i,j]
  }
}

S.oc <- S[111:223, 111:223]
S.oc <- S.oc/(res2-res1+1)
```

```{r}
longData<-melt(S.oc)
longData<-longData[longData$value!=0,]

#o <- seriate(S.oc, method = "BEA_TSP")
#longData$Var1 <- factor(longData$Var1, levels=names(unlist(o[[1]][])))
#longData$Var2 <- factor(longData$Var2, levels=names(unlist(o[[1]][])))

ord <- read.csv("ordering_occup.csv")

longData$Var1 <- factor(longData$Var1, levels=ord[,2])
longData$Var2 <- factor(longData$Var2, levels=ord[,2])

cl <- data.frame(names(unlist(ord[[1]][])))
cl <- data.frame(ord[,2])
colnames(cl)[1] <- "occupations"
cl$occupations <- as.character(cl$occupations)

clust2 <- data.frame(rownames(clust), clust[,30])
rownames(clust2) <- 1:223
colnames(clust2) <- c("programs", "clusters")

cl <- left_join(cl, clust2, by=c("occupations"="programs"))

#color palette for axis
axis.x.colour <- (cl[,2] %>% plyr::mapvalues(from=c(1:10), to=c("#B40404", "#e68a00", "#0B6121", "#000099", "#0099cc", "#00cc99", "#6600cc", "#e600e6", "#999900", "#7094db")))

#ordering <- names(unlist(o[[1]][]))
#write.csv(ordering, "ordering_occup.csv")
```

```{r}
ggplot(longData, aes(x = Var2, y = Var1)) + 
  geom_raster(aes(fill=value)) + 
  scale_fill_gradient(low="grey60", high="red") +
  labs(x="", y="", title="") +
  theme_bw() + 
  theme(axis.text.x=element_text(size=5, angle=90, vjust=0.2, hjust=1),
                     axis.text.y=element_text(size=5),
                     legend.text=element_text(size=8),
                     legend.title=element_text(size=8)) +
  theme(axis.text.x=element_text(colour=axis.x.colour)) +
  theme(axis.text.y=element_text(colour=axis.x.colour)) +
  annotate("segment", x = 20.5, xend = 20.5, y = 0, yend = 113.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 42.5, xend = 42.5, y = 0, yend = 113.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 68.5, xend = 68.5, y = 0, yend = 113.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 84.5, xend = 84.5, y = 0, yend = 113.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 113.5, y = 20.5, yend = 20.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 113.5, y = 42.5, yend = 42.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 113.5, y = 68.5, yend = 68.5, colour = "blue", size = 0.5) +
  annotate("segment", x = 0, xend = 113.5, y = 84.5, yend = 84.5, colour = "blue", size = 0.5)


#ggsave("oc_Fig_2.9-3.4_v2.pdf", height = 22, width=23, units="cm")
```




